---
title: "Resampling and regularization Homework"
author: "Jiachen Feng"
date: "2021/2/12"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 5.8
(a)
```{r}
set.seed(1)
x <- rnorm(100)
y <- x-2*x^2+rnorm(100)
```
n is 100, p is 2. $$y=x-x^2+\epsilon$$

(b)
```{r}
plot(x,y,pch=20)
```
The scatterplot is like a quadratic function.

(c)
```{r}
library(boot)
set.seed(100)
data <- data.frame(x,y)
mod1 <- glm(y~x)
cv.glm(data,mod1)$delta[1]

mod2 <- glm(y~poly(x,2))
cv.glm(data,mod2)$delta[1]

mod3 <- glm(y~poly(x,3))
cv.glm(data,mod3)$delta[1]

mod4 <- glm(y~poly(x,4))
cv.glm(data,mod4)$delta[1]
```

(d)
```{r}
set.seed(200)
mod1 <- glm(y~x)
cv.glm(data,mod1)$delta[1]

mod2 <- glm(y~poly(x,2))
cv.glm(data,mod2)$delta[1]

mod3 <- glm(y~poly(x,3))
cv.glm(data,mod3)$delta[1]

mod4 <- glm(y~poly(x,4))
cv.glm(data,mod4)$delta[1]
```
Same.

(e)
model 2. The function is quadratic, so that this model fits best.

(f)
```{r}
summary(mod1)
summary(mod2)
summary(mod3)
summary(mod4)
```
All of the four models are statistically significant.

## 6.2
(a)
i. Wrong.
ii. Wrong.
iii. Right.
iv. Wrong.
It is less flexible because the complexity of lasso is related to $\lambda$.

(b)
Ridge regression is less flexible and hence will give improved prediction accuracy when its increase in bias is less than its decrease in variance.

(c)
Non-linear methods are more flexible and hence will give improved prediction accuracy when its increase in variance is less than its decrease in bias.

## 6.10
(a)
```{r}
set.seed(1000)
mat <- matrix(rnorm(1000 * 20), 1000, 20)
p <- rnorm(20)
p[1] <- 0
p[2] <- 0
p[3] <- 0
epsilon <- rnorm(1000)
y <- mat %*% p + epsilon
```

(b)
```{r}
set.seed(1000)
mat1 <- matrix(rnorm(100 * 20), 100, 20)
p1 <- rnorm(20)
p1[1] <- 0
p1[2] <- 0
p1[3] <- 0
epsilon1 <- rnorm(100)
train <- mat1 %*% p1 + epsilon1

mat2 <- matrix(rnorm(900 * 20), 900, 20)
p2 <- rnorm(20)
p2[1] <- 0
p2[2] <- 0
p2[3] <- 0
epsilon2 <- rnorm(900)
test <- mat2 %*% p2 + epsilon2

```

(c)
```{r}

```

